---
title: "Week 1 Notes"
author: "Weijia Chen"
date: "21 September 2014"
output: html_document
---

###Quick questions for Installing R
Standard Deviation Fomula:
$s = \sqrt{\frac{1}{N-1}\sum_{i=1}^{N} (x_{i}-\bar{x})^2}$
```{r}
sd(c(5,8,12))
m <- mean(c(5,8,12))
sqrt(((5-m)^2 + (8-m)^2 + (12-m)^2)/(3-1))
```

```{r}
which.min(c(4,1,6))
```
###Quick question 1
University of Auckland was the first version of R developed.

###Quick question 2
##### Rules of naming objects in R
* Don't use spaces or underscores in object name
* Don's start object name with a number
* Object names are case sensitive. Capital and lowercase letters are different.

###Quick question 3
1. Quotes **_""_** changes all values' class to **_Character_**
```{r}
x <- c("apple","1", "3.14")
x
class(x)
```

2. `rbind` can add new observations to existing dataset. New row (rows) will be added in the bottom
```{r}
d <- data.frame(V1 = 1:2, V2 = 4:5,V3 = 7:8)
n <- c(3,6,9)
d <- rbind(d,n)
d
```

3. `data.frame` can combine vectors to data frame
```{r}
x <- c(1:3);y <- c(4:6);z <- c(7:9)
combine <- data.frame(x,y,z)
combine
class(combine)
```
4. `cbind` can add new variable to the existing data frame
```{r}
x <- c(1:3);y <- c(4:6);z <- c(7:9)
combine <- data.frame(x,y);combine #3*2 dimensions
combine <- cbind(combine, z) # add thrid col z to combine
combine
```

###Quick question 4
1.`str()` and `dim()` can explore how many rows and observations in data frame (dimensions)
```{r}
str(combine)
dim(combine)
```
2. `mean()` function can calculate the average of a vector, `summary()` function can calculates the big five (min, 1QI, median, mean,3QI, max) of each variable (col)
```{r}
d <- data.frame(V1 = 1:100, V2 = 2:101,V3 = 3:102)
summary(d)
```
3. `sd()` function can calculate the standard deviation of a vector
```{r}
x <- c(1:100)
mean(x)
sd(x)
```
4. **WHO_Europe** is not recommended as a object name

###Quick question 5
1. Mean of Over60
```{r}
who <- read.csv("WHO.csv")
names(who)
mean(who$Over60)
```
2. Which country has the smallest percentage of the population over 60?
```{r}
library(dplyr)
who <- tbl_df(who)
who <- select(who, Country, Population, Over60, LiteracyRate)
whoc <- arrange(who, desc(Over60))
tail(whoc)
```
3. Which country has the largest literacy rate?
```{r}
whol <- arrange(who, desc(LiteracyRate))
head(whol)
```

